

\section{Cell Cycle}

\begin{enumerate}
	\item G1 PHASE:[(a) p21 (b) p27] AFFECT [(a) Cyclin D1 (b) CDK4/6] INHIBITED by [(a) NS-398 (MC26), (b) Celecoxib (K562), (c) DUP-697 (K562)]. \cite{key4000}
\end{enumerate}


\section{References}


\subsection{KEGG}

\bibitem[400]{key4000} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).

\bibitem[401]{key4001} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).

\bibitem[402]{key4002} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000). 

\subsection{Biology}

\bibitem[600]{key6000} Rouillard AD, Gundersen GW, Fernandez NF, Wang Z, Monteiro CD, McDermott MG, Ma'ayan A. 
\newblock The harmonizome: a collection of processed datasets gathered to serve and mine knowledge about genes and proteins. 
\newblock Database (Oxford). 2016 Jul 3;2016. pii: baw100.

\bibitem[601]{key6001}Szklarczyk, D., Franceschini, A., Wyder, S., Forslund, K., Heller, D., Huerta-Cepas, J., … von Mering, C. (2015). 
\newblock STRING v10: protein–protein interaction networks, integrated over the tree of life. 
\newblock Nucleic Acids Research, 43(Database issue), D447–D452. http://doi.org/10.1093/nar/gku1003

\bibitem[602]{key6002} https://string-db.org/

\bibitem[603]{key6003}https://signor.uniroma2.it/

