
\section{R Application Programming Interfaces (APIs)}

The following list of R packages\cite{key1000} with the bioconductor API were used in this short example. \textbf{ Basic:} readr \cite{key1001},xtable \cite{key1002},tm \cite{key1003} and \cite{key1004},topicModels \cite{key1005},wordcloud \cite{key1006}, stringi \cite{key1007} and stringr \cite{key1008}.  For \textbf{scientific visualization:} phaseR \cite{key2001}, corrplot \cite{key2002}, plot3D \cite{key2003}, scatterplot3D \cite{key2004}, rgl \cite{key2005} and visNetwork \cite{key2006} and ggtern \cite{key2007}. For \textbf{Mathematics and Statistics} deTestSet \cite{key3001}, deSolve \cite{key3002}, ReacTran \cite{key3003} and \cite{key3004}, rootSolve \cite{key3005}, PearsonDS \cite{key3006},igraph \cite{key3007},fda \cite{key3008},tSeriesChaos \cite{key3009}, boot \cite{key3010},sampling \cite{key3011} and \cite{key3012}, pracma \cite{key3013}, fitdistrplus \cite{key3014}, combinat \cite{key3015}, actuar \cite{key3016} Matrix \cite{key3017} and changepoint \cite{key3018}.  For \textbf{Genomics} KEGGgraph \cite{key4001}, \cite{key4002} and \cite{key4003}

\section{References}

\bibliographystyle{plain}
\begin{thebibliography}{00}
	\tiny
	\subsection{R Packages}
	
	\bibitem[100]{key1000}R Core Team (2015). 
	\newblock R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
	\newblock URL https://www.R-project.org/.
	
	\bibitem[101]{key1001} Hadley Wickham, Jim Hester and Romain Francois (2017). readr: Read
	\newblock Rectangular Text Data. R package version 1.1.1.
	\newblock https://CRAN.R-project.org/package=readr
	
	\bibitem[102]{key1002} David B. Dahl (2016). 
	\newblock xtable: Export Tables to LaTeX or HTML. R package version 1.8-2.
	\newblock https://CRAN.R-project.org/package=xtable
	
	\bibitem[103]{key1003}  Feinerer and Kurt Hornik (2017).
	\newblock tm: Text Mining Package. 
	\newblock R package version 0.7-1. https://CRAN.R-project.org/package=tm
	
	\bibitem[104]{key1004}  Feinerer, Kurt Hornik, and David Meyer (2008). 
	\newblock Text Mining Infrastructure in R. 
	\newblock Journal of Statistical Software 25(5): 1-54. URL:http://www.jstatsoft.org/v25/i05/.
	
	\bibitem[105]{key1005} B and Hornik K (2011).
	\newblock topicmodels: An R Package for Fitting Topic Models.
	\newblock Journal of Statistical Software, *40*(13), pp. 1-30. doi:10.18637/jss.v040.i13 (URL:http://doi.org/10.18637/jss.v040.i13).
	
	\bibitem[106]{key1006} Ian Fellows (2014). 
	\newblock wordcloud: Word Clouds. R package version 2.5.
	\newblock https://CRAN.R-project.org/package=wordcloud
	
	\bibitem[107]{key1007} Gagolewski M. and others (2017). 
	\newblock R package stringi: Character string processing facilities. 
	\newblock http://www.gagolewski.com/software/stringi/.DOI:10.5281/zenodo.32557
	
	\bibitem[108]{key1008} Hadley Wickham (2017).
	\newblock stringr: Simple, Consistent Wrappers for Common String Operations. 
	\newblock R package version 1.2.0. https://CRAN.R-project.org/package=stringr
	
\subsubsection{Bioconductor: Genomics}
	
	
\subsubsection{Scientific Visualization}
	
	\bibitem[201]{key2001}Michael J. Grayling (2014). 
	\newblock phaseR:Phase Plane Analysis of One and Two Dimensional Autonomous ODE Systems. 
	\newblock R package version 1.3. https://CRAN.R-project.org/package=phaseR
	
	\bibitem[202]{key2002} Wei and Viliam Simko (2016).
	\newblock corrplot: Visualization of a Correlation Matrix. 
	\newblock R package version 0.77. https://CRAN.R-project.org/package=corrplot
	
	\bibitem[203]{key2003} Soetaert (2017). 
	\newblock plot3D: Plotting Multi-Dimensional Data. 
	\newblock R package version 1.1.1. https://CRAN.R-project.org/package=plot3D
	
	\bibitem[204]{key2004} Ligges, U. and Mächler, M. (2003).
	\newblock Scatterplot3d - an R Package for Visualizing Multivariate Data.
	\newblock Journal of Statistical Software 8(11), 1-20.
	
	\bibitem[205]{key2005}Daniel Adler, Duncan Murdoch and others (2017). 
	\newblock rgl: 3D Visualization Using OpenGL. 
	\newblock R package version 0.98.1. https://CRAN.R-project.org/package=rgl
	
	\bibitem[206]{key2006} Almende B.V., Benoit Thieurmel and Titouan Robert (2017). visNetwork:
	\newblock Network Visualization using 'vis.js' Library. R package version 2.0.1.
	\newblock https://CRAN.R-project.org/package=visNetwork
	
	\bibitem[207]{key2007} Nicholas Hamilton (2017). 
	\newblock ggtern: An Extension to 'ggplot2', for the Creation of Ternary Diagrams. 
	\newblock R package version 2.2.1. https://CRAN.R-project.org/package=ggtern
	
\subsubsection{Mathematics and Statistics}
	
	\bibitem[301]{key3001} Karline Soetaert, Jeff Cash and Francesca Mazzia (2016). 
	\newblock deTestSet: Testset for Differential Equations. R package version 1.1.3.
	\newblock http://CRAN.R-project.org/package=deTestSet
	
	\bibitem[302]{key3002}Karline Soetaert, Thomas Petzoldt, R. Woodrow Setzer (2010). 
	\newblock Solving Differential Equations in R: Package deSolve. 
	\newblock Journal of Statistical Software, 33(9), 1--25. URL http://www.jstatsoft.org/v33/i09/ DOI 10.18637/jss.v033.i09
	
	\bibitem[303]{key3003}Soetaert, Karline and Meysman, Filip, (2012).
	\newblock Reactive transport in aquatic ecosystems: Rapid model prototyping in the open source software R
	\newblock Environmental Modelling and Software, 32, 49-60.
	
	\bibitem[304]{key3004}Soetaert K. and P.M.J. Herman (2009).  
	\newblock A Practical Guide to Ecological Modelling. 
	\newblock Using R as a Simulation Platform.  Springer, 372 pp.
	
	\bibitem[305]{key3005}Soetaert K. (2009).  
	\newblock rootSolve: Nonlinear root finding, equilibrium and steady-state analysis of ordinary differential equations.  
	\newblock R-package version 1.6.
	
	\bibitem[306]{key3006}Martin Becker and Stefan Klößner (2016). 
	\newblock PearsonDS: Pearson Distribution System. 
	\newblock R package version 0.98. http://CRAN.R-project.org/package=PearsonDS
	
	\bibitem[307]{key3007}Csardi G, Nepusz T (2006).
	\newblock The igraph software package for complex network research,
	\newblock  InterJournal, Complex Systems 1695. 2006. http://igraph.org
	
	\bibitem[308]{key3008} J. O. Ramsay, Hadley Wickham, Spencer Graves and Giles Hooker (2017). 
	\newblock fda:Functional Data Analysis. 
	\newblock R package version 2.4.7. https://CRAN.R-project.org/package=fda
	
	\bibitem[309]{key3009} Antonio and Fabio Di Narzo (2013).
	\newblock tseriesChaos: Analysis of nonlinear time series. 
	\newblock R package version 0.1-13.https://CRAN.R-project.org/package=tseriesChaos
	
	\bibitem[310]{key3010} Angelo Canty and Brian Ripley (2017). 
	\newblock boot: Bootstrap R (S-Plus) Functions. 
	\newblock R package version 1.3-20.
	
	\bibitem[311]{key3011}Yves Tillé and Alina Matei (2016). 
	\newblock sampling: Survey Sampling. 
	\newblock R package version 2.8. https://CRAN.R-project.org/package=sampling
	
	\bibitem[312]{key3012} Davison, A. C. and Hinkley, D. V. (1997) 
	\newblock Bootstrap Methods and Their Applications. 
	\newblock Cambridge University Press, Cambridge. ISBN 0-521-57391-2.
	
	\bibitem[313]{key3013}Hans Werner Borchers (2017). 
	\newblock pracma: Practical Numerical Math Functions. 
	\newblock R package version 2.0.7. https://CRAN.R-project.org/package=pracma
	
	\bibitem[314]{key3014}Marie Laure Delignette-Muller, Christophe Dutang (2015). 
	\newblock fitdistrplus:An R Package for Fitting Distributions. 
	\newblock Journal of Statistical Software, 64(4), 1-34. URL http://www.jstatsoft.org/v64/i04/.
	
	\bibitem[315]{key3015} Scott Chasalow (2012). 
	\newblock combinat: combinatorics utilities. 
	\newblock R package version 0.0-8. https://CRAN.R-project.org/package=combinat
	
	\bibitem[316]{key3016} C. Dutang, V. Goulet and M. Pigeon (2008). 
	\newblock actuar: An R Package for Actuarial Science. 
	\newblock Journal of Statistical Software, vol. 25, no. 7, 1-37. URL http://www.jstatsoft.org/v25/i07
	
	\bibitem[317]{key3017} Douglas Bates and Martin Maechler (2017). 
	\newblock Matrix: Sparse and Dense Matrix Classes and Methods. 
	\newblock R package version 1.2-11.https://CRAN.R-project.org/package=Matrix
	
	\bibitem[318]{key3018} Killick R, Haynes K and Eckley IA (2016).
	\newblock changepoint: An R package for changepoint analysis. R package version
	\newblock 2.2.2, <URL: https://CRAN.R-project.org/package=changepoint>.
	
\subsection{Genomics}
	
	\bibitem[400]{key4000} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
	\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
	\newblock Nucleic Acids Res. 45, D353-D361 (2017).
	
	\bibitem[401]{key4001} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
	\newblock KEGG as a reference resource for gene and protein annotation. 
	\newblock Nucleic Acids Res. 44, D457-D462 (2016).
	
	\bibitem[402]{key4002} Kanehisa, M. and Goto, S.; 
	\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
	\newblock Nucleic Acids Res. 28, 27-30 (2000). 
	

\subsection{Noise}

	\bibitem[500]{key5000} J. Timmer and M. König (1995): 
	\newblock On generating power law noise. 
	\newblock Astron. Astrophys. 300, 707-710.
	
	
\subsection{Biology Links}

\bibitem[603]{key6000} Rouillard AD, Gundersen GW, Fernandez NF, Wang Z, Monteiro CD, McDermott MG, Ma'ayan A. 
\newblock The harmonizome: a collection of processed datasets gathered to serve and mine knowledge about genes and proteins. 
\newblock Database (Oxford). 2016 Jul 3;2016. pii: baw100. 

	
\end{thebibliography}

