%-------------------Example Student Reading List, Mathematical Note taking for the Classroom, and Lecture Designs
%-------------------for Independent Reading and Seminars for Students
\section{References}

\bibitem[100]{key100}Chou (1976)
\newblock The Median-Effect Equation
\newblock Journal of Theoretical Biology 59:253-276 

\bibitem[200]{key200}Brown, R. D., and Martin, Y. C. (1997). 
\newblock Designing combinatorial library mixtures using a genetic algorithm. 
\newblock Journal of Medicinal Chemistry, 40, 2,304–2,313.

\bibitem[902]{key902}Jeroen de Keijze, Bela M. Mulder and Marcel E. Janson (2014)
\newblock Microtubule networks for plant cell division
\newblock Syst Synth Biol 8:187–194 DOI 10.1007/s11693-014-9142-x

\bibitem[900]{key900} Ambrose   C,   Wasteneys   GO   (2012)   
\newblock Nanoscale  and  geometric influences  on  the  microtubule  cytoskeleton  in  plants:  thinking inside  and  outside  the  box.  
\newblock Protoplasma  249(Suppl):S69–S76. doi:10.1007/s00709-011-0334-x

\bibitem[901]{key901} Wightman   R,   Chomicki   G,   Kumar   M   et   al   (2013)   
\newblock SPIRAL2 determines plant microtubule organization by modulating microtubule severing. 
\newblock Curr Biol 23:1902–1907

\bibitem[300]{key300}Tahara, T., Arisawa, T., Shibata, T., Hirata, I., and Nakano, H. (2007). 
\newblock Analysis of Beta-Tubulin Gene Exon 4 Mutations in Advanced Stage III or IV Gastric Cancer. 
\newblock Journal of Clinical Biochemistry and Nutrition, 40(3), 210–215. http://doi.org/10.3164/jcbn.40.210

\bibitem[500]{key500}Dong, P., and Liu, Z. (2017). 
\newblock Shaping development by stochasticity and dynamics in gene regulation. 
\newblock Open Biology, 7(5), 170030. http://doi.org/10.1098/rsob.170030

\bibitem[501]{key501}Kobayashi et al., 
\newblock Controlling Cell Fate Specification System by Key Genes Determined from Network Structure,
\newblock iScience (2018), https://doi.org/10.1016/j.isci.2018.05.004

\bibitem[400]{key400} Christian Garavaglia, Franco Malerba, Luigi Orsenigo, Michele Pezzoni
\newblock Innovation and Market Structure in Pharmaceuticals An Econometric Analysis on Simulated Data
\newblock Jahrbücher für Nationalökonomie und Statistik  April 2014

\bibitem[401]{key401} http://www.worldpharmanews.com/research-and-development

\subsection{Gene Networks}
	

\subsection{Cancer Reports}
	
\bibitem[600]{key7000} National Cancer Institute
\newblock Annual Plan and Budget Proposal FY 2019
\newblock https://www.cancer.gov/about-nci/budget/plan 


\subsection{NCI-60 Cell Line}

\bibitem[700]{key7001}Reinhold, W.C., et al. (2012) 
\newblock CellMiner: a web-based suite of genomic and pharmacologic tools to explore transcript and drug patterns in the NCI-60 cell line set. 
\newblock Cancer Research, 72, 3499-3511.

\bibitem[701]{key7002}Sousa, F.G., et al. (2015) 
\newblock Alterations of DNA repair genes in the NCi-60 cell lines and their predictive value for anticancer drug activity. 
\newblock DNA Repair 28 (2015) 107-115.

\bibitem[702]{key7003}Varma, S., et al. (2014) 
\newblock High Resolution Copy Number Variation Data in the NCI-60 Cancer Cell Lines from Whole Genome Microarrays Accessible through CellMiner. 
\newblock PLoS ONE 9(3): e92047.

\bibitem[703]{key7004} Luna A et al. rcellminer: Exploring Molecular Profiles and
\newblock Drug Response of the NCI-60 Cell Lines in R. Bioinformatics.
\newblock 2015 Dec. http://www.ncbi.nlm.nih.gov/pubmed/26635141

\bibitem[1000]{key1000}Karim Mezhoud (2017). bioCancer: Interactive Multi-Omics
\newblock Cancers Data Visualization and Analysis. R package version
\newblock 1.4.0. http://kmezhoud.github.io/bioCancer

\bibitem[1001]{key1001}Ti-Tai Wang, Tzu-Pin Lu, Chien-Yueh Lee, Liang-Chuan Lai, Mong-Hsun Tsai, and Eric Y. Chuang (2016). 
\newblock anamiR--an integrated analysis package of miRNA and mRNA expression.
\newblock Manuscript submitted for publication.

\bibitem[1002]{key1002}Sacha Epskamp, Angelique O. J. Cramer, Lourens J. Waldorp, Verena D. Schmittmann, Denny Borsboom (2012). 
\newblock qgraph: Network Visualizations of Relationships in Psychometric Data. 
\newblock Journal of Statistical Software, 48(4), 1-18. URL http://www.jstatsoft.org/v48/i04/.



